Leveraging Diversity to Find Bugs in JavaScript Engines

### 2019-02-19 paper/paper.tex
pass on RQ1

The ECMA Test262~\cite{ecma262-conformance-suite} test suite serves to check conformance of
engines to the \js\ current standard. As it is acceptable to release
engines fulfilling the specification only partially~\cite{kangax}, it
is expected that engines do not fully pass this check. However, we
expect that results provide indication of engine's maturity. In the
limit, it is not desirable to flood bug reports on engines at early
stages of development. We ran the suite once a day for seven
consecutive days from the period of a week and averaged the passing ratios.

\begin{wraptable}[10]{r}{0.22\textwidth}
%  \vspace{-2ex}      
  \centering
  \caption{\label{tab:test262}Percentage of passing tests on
    the Test262 conformance suite.}
  \vspace{-2ex}        
  \small
  \begin{tabular}{crr}
    \toprule
    engine & \% passing \\
    \midrule
    \jsc{} & 92\%\\
    \veight{} & 95\% \\
    \chakra{} & 75\% \\    
    \smonkey{} & 93\% \\
    \bottomrule
  \end{tabular}
  \normalsize
  \vspace{-4ex}
\end{wraptable}
Table~\ref{tab:test262} shows the average number of passing tests over
this period. The variance of results was negligible; for that reasons,
we omitted standard deviations. We noticed that all four engines but
\chakra{} used some variant of the Test262 suite as part of their
regression process, but we used the same version in this
experiment~\cite{ecma262-conformance-suite}. Results show that there
are still many unsupported cases as can be observed from the
percentages in the table, but the number of passing tests is high,
with \veight\ and \smonkey\ performing better compared to others and
\chakra\ performing well worse than others. It is important to
highlight that failures in this conformance test suite indicates
missing features as opposed to bugs. However, note that \chakra\ is
both the engine that has the lowest passing ratio in the conformance
test suite and the one we were able to find more bugs. Although it is
plausible to find correlation between the passing ratios and
reliability as measured by the number of bugs found (as per
Figure~\ref{fig:summary}), we not not imply causality.

\begin{center}
  \fbox{
    \begin{minipage}{8cm}
      \textit{Summary:}~All engines seems to adhere well to the
      \js\ standard. Except for \chakra, the passing ratio of all
      engines is above 90\%.
      \end{minipage}
    }
\end{center}

>>>>

The ECMA Test262~\cite{ecma262-conformance-suite} test suite serves to
check conformance of engines to the \js\ standard. It is
acceptable to release engines fulfilling the specification only
partially~\cite{kangax}. We expect that the pass rate on this suite
provide some indication of the engine's maturity. In the limit, it is
not desirable to flood bug reports on engines at early stages of
development.

\begin{wraptable}[10]{r}{0.22\textwidth}
%  \vspace{-2ex}      
  \centering
  \caption{\label{tab:test262}Percentage of passing tests on
    the Test262 conformance suite.}
  \vspace{-2ex}        
  \small
  \begin{tabular}{crr}
    \toprule
    engine & \% passing \\
    \midrule
    \jsc{} & 92\%\\
    \veight{} & 95\% \\
    \chakra{} & 75\% \\    
    \smonkey{} & 93\% \\
    \bottomrule
  \end{tabular}
  \normalsize
  \vspace{-4ex}
\end{wraptable}
For this experiment, we ran the suite once a day for seven consecutive
days and averaged the passing ratios. Table~\ref{tab:test262} shows
the average number of passing tests over this period. The variance of
results was negligible; for that reason, we omitted standard
deviations. We noticed that all four engines but \chakra{} used some
variant of the Test262 suite as part of their regression process, but
we used the same version in this
experiment~\cite{ecma262-conformance-suite}. Results show that there
are still many unsupported scenarios as can be observed from the
percentages in the table. The number of passing tests is high and
similar for \jsc{}, \veight{}, and \smonkey\ whereas \chakra\ performs
worse compared to the other engines. Note also that \chakra\ is both
the engine that has the lowest passing ratio in this test suite and
the one we were able to find more bugs (as per
Figure~\ref{fig:summary}). Although it is plausible to find
correlation between the passing ratios and reliability as measured by
the number of bugs found, we do not imply causality. It is important
to note that failures in this conformance test suite indicates missing
features as opposed to bugs.

\begin{center}
  \fbox{
    \begin{minipage}{8cm}
      \textit{Summary:}~All engines seem to adhere well to the
      \js\ standard. Except for \chakra, the passing ratio of all
      engines is above 90\%.
      \end{minipage}
    }
\end{center}
